\documentclass{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{authblk} %package for blocking authors, followed by blocking affiliation
\usepackage{url}
\usepackage{ulem} % when using ulem package, must change \emph to \it for italics.
\usepackage{hyperref}
\usepackage{array}
\usepackage{amssymb,amsmath,tabu}
\usepackage{hyperref}
\usepackage[super]{nth}
\setlength\parindent{0pt}
\usepackage[english]{babel}


\begin{document}
\title{Homework 4\\ SOCI 303: Statistics for the Social Sciences (Spring 2017) \\ {\large{10 points}} \\ {\large{Due: May 12, 2017}}}
\author[*]{}
\date{}
\maketitle



\section*{Overview:}
In this assignment, you'll be completing problems using R. These problems cover topics from Chapters 9 and 12 in your textbook. \textbf{Remember to append/copy and paste your R script as the final page of this assignment} (as a new page).

\subsection*{Problem 1}
\begin{itemize}
\item What do both t-tests and ANOVA test (e.g. what is similar about t-test and ANOVA)?
\end{itemize}


\subsection*{Problem 2 (\textit{T-test})}
\begin{itemize}
\item Using the \texttt{surveys} data set in R (from the \texttt{MASS} package), report the \textbf{means} for the (\texttt{Height}) variable, broken out by the (\texttt{Sex}) grouping variable.
\item Using the \texttt{surveys} data set in R (from the \texttt{MASS} package), report the \textbf{standard deviations} for the (\texttt{Height}) variable, broken out by the (\texttt{Sex}) grouping variable.
\item Fully/correctly report and interpret the T-test.
\item Based on the means reported above, which group (\texttt{Sex}) is taller in \texttt{Height}?
\end{itemize}

\subsection*{Problem 3 (\textit{Analysis of Variance})}
\begin{itemize}
\item Using the \texttt{surveys} data set in R (from the \texttt{MASS} package), report the \textbf{means} for the (\texttt{Pulse}) variable, broken out by their level of exercise (\texttt{Exer}), the grouping variable.
\item Using the \texttt{surveys} data set in R (from the \texttt{MASS} package), report the \textbf{standard deviations} for the (\texttt{Pulse}) variable, broken out by their level of exercise (\texttt{Exer}), the grouping variable.
\item Fully/correctly report and interpret the ANOVA.
\item Based on the means reported above, which group(s) (\texttt{Exer}) has/have a higher in \texttt{Pulse}?
\end{itemize}

\subsection*{Problem 4}
\begin{itemize}
\item When should we use a T-test and when should we use an ANOVA?
\end{itemize}

\end{document}











